LG5 Function Errata

### 2020-10-26 doc/LG5_errata/LG5_errata.Rmd
fixed broken link

$$
dbh = \frac{K-L}{1 + 1/\theta*\exp(-r(doy - doy_{ip})/\theta)^{\theta}}
$$
However the `lg5.pred()` function from the [`RDendrom`
package](https://github.com/seanmcm/RDendrom/blob/master/R/DENDRO_BASE_FUNCTIONS.R#L544) computes DBH as follows:

>>>>

$$
dbh = \frac{K-L}{1 + 1/\theta*\exp(-r(doy - doy_{ip})/\theta)^{\theta}}
$$
However the `lg5.pred()` function from the [`RDendrom`
package](https://github.com/seanmcm/RDendrom/blob/master/R/DENDRO_BASE_FUNCTIONS.R) computes DBH as follows:
